---
title: |
  Hackathon 2023 \
  Task 1.1
author: |
  Author: Giorgio Coppola \
  Email: g.coppola@students.hertie-school.org \
  Group: Armande Aboudrar-Meda, Giorgio Coppola, Giulia Petrilli, Luca Vellage
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
  pdf_document:
    toc: no
---

```{=html}
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>
```

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)

options(scipen = 999)
```

```{r, include = F}
pacman::p_load(tidyverse, leaflet, tigris, sf, haven, RColorBrewer)
```

<br>

------------------------------------------------------------------------

## Subtask 1 - Interactive map of survey entries

Create an interactive leaflet map divided by inputstates that are colored in relation to a total number of survey responses across all waves, following good practice of visualization. For this plot, you should:

• employ a color palette based on the number range of survey entries.

• use the OpenStreetMap.Mapnik provider tile.

• create a popup that reads “Total survey responses for {inputstate initials}: {Number}”.

• add a color legend with a title.

<br>

**Load data**
```{r}
survey_data <- readRDS("./survey/meof_usa_survey_df.rds")
survey_data <- haven::as_factor(survey_data) 
```

**Get geodata for US**
```{r, echo = TRUE, results = 'hide'}
# get geodata for the US state we are interested into
states_sf <- tigris::states(cb = TRUE, class = "sf")
```

**Get number of responses for each each state**
```{r}
# filter the rows in the states_sf data frame based on whether the values in the 
# "NAME" column are present in the unique_states vector (matching state_sf with unique_States)
unique_states <- unique(survey_data$inputstate)
states_sf <- states_sf[states_sf$NAME %in% unique_states, ] 

# get the number of responses for each state
survey_data_map <- survey_data |> 
  group_by(inputstate) |> 
  summarize(num_responses = n()) # assuming that each row is a unique response

# check if the number of responses match:
# sum(survey_data_map$num_responses)
# the number should be equal to the number of observations in the original dataset,
#  and it is: both are 10200 (number of rows).
```

**Add percentages**
```{r}
# add percentage of responses to the survey_data_map
total_responses <- sum(survey_data_map$num_responses)
survey_data_map <- survey_data_map |> 
  mutate(percentage = round((num_responses / total_responses) * 100, 2))

# join map data with spatial data (including percentages)
map_df <- left_join(states_sf, survey_data_map, by = c("NAME" = "inputstate"))
map_df <- st_transform(map_df, crs = 4326) # solve warning
```

**Create map**
```{r}
# create a color palette function based on the range of num_responses
max <- max(map_df$num_responses)
min <- min(map_df$num_responses)

bins <- c(min, 20, 50, 100, 200, 400, 600, 800, max)
pal <- colorBin("YlGn", domain = map_df$num_responses, bins = bins)

# Create the leaflet map
map <- leaflet(map_df) %>% 
  setView(lng = -95.7129, lat = 37.0902, zoom = 2.5) %>% 
  addProviderTiles(providers$OpenStreetMap.Mapnik) %>% 
  addPolygons(
    fillColor = ~pal(num_responses),
    weight = 0.8,
    opacity = 2,
    color = "lightgrey",
    dashArray = "NULL",
    fillOpacity = 0.7,
    popup = ~paste("Total survey responses for", NAME, ":", num_responses, 
                   "<br>Percentage of Total:", sprintf("%.2f%%", percentage))) |> 
  addLegend(
    pal = pal, 
    values = ~num_responses, 
    opacity = 0.7, 
    title = "Number of Responses",
    position = "bottomright")
```

**Visualize map**
```{r, fig.show="hold", out.width="85%", fig.align="center", warning=F, echo=F}
map
```

<br>