---
title: |
  Hackathon 2023 \
  Task 1.2
author: |
  Author: Varvara Ilyina \
  Email: v.ilyina@students.hertie-school.org \
  Group: Armande Aboudrar-Meda, Giorgio Coppola, Giulia Petrilli, Luca Vellage
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: FALSE
    theme: lumen
    toc: TRUE
    toc_depth: 3
    toc_float: true
---

<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

***

* Write a function to explore the distribution of answers for a given question on each of the survey waves.
* The function should:
  * take the data frame and survey item as arguments.
  * return a small multiple barplot grouped at the survey wave-level with the answer
  option counts (including NAs as a separate category).
  * present the original survey question (label) and the variable name in the title of the plot, and the data source in a footnote below the plot.
  * graph the value labels in the answer tick axis.
  * have an additional argument that lets the user determine whether absolute numbers (counts) or relative shares (in % of respondents) are reported.
  * stop if the input variable is not a labelled <dbl+lbl> type.
* Prove the correct behavior of the function with at least three survey questions, highlighting that the arguments work as intended on (and only on) valid variable types.

***

## Setup

### Import data
```{r, include = TRUE}

## load packages
pacman::p_load(tidyverse, readr, haven, sjlabelled, RColorBrewer)

## load survey data
data_survey <- read_rds("./survey/meof_usa_survey_df.RDS")
data_survey_factor <- read_rds("./survey/meof_usa_survey_df.RDS") %>% haven::as_factor()

## load tracking data
data_tracking <- read_rds("./tracking/meof_usa_web_df.RDS")

```
<br>

### Specify open-ended variables
```{r, echo = TRUE, results = 'asis'}

## manually find open-ended vars
open_vars <- c("mip", "mip2", "tolerance_list_prime_att_text", "hatelaw_frame_attention_check_text")

## choose vars with many responses
long_vars <- data.frame(
  var_name = names(data_survey),
  unique_counts = sapply(data_survey, function(x) length(unique(x)))
) %>%
  arrange(-unique_counts) %>%
  filter(unique_counts > 400) %>%
  pull(var_name)

## vector with open-ended vars
open_vars <- c(open_vars, long_vars)

```
<br>

***

## Generate function
```{r, echo = TRUE}

## write a super cool function
super_cool_function <- function(df_input, var_input, share) {
  
  ## retrieve df
  df_raw <- get(df_input)
  
  
  ## check for correct df
  if(df_input != "data_survey") {
    stop(paste("This dataset cannot be used. Please select an appropriate dataset input."))
  }
  
  
  ## check if var in df
  if(!var_input %in% names(df_raw)) {
    stop(paste("The variable", var_input, "is not in the", df_input, "data frame."))
  }
  
  
  ## check if var is a discrete choice question
  if(var_input %in% open_vars) {
    stop(paste("The variable", var_input, "is not a discrete choice question."))
  }
  
  
  ## check class of var
  var_type <- df_raw %>%
    select(!!var_input) %>%
    pull() %>%
    class()
  
  
  ## check if var is labelled and numeric
  if(!any(c("haven_labelled", "double") %in% var_type)) {
    stop(paste("The variable", var_input, "is not a labelled numeric variable of class 'dbl+lbl'."))
  }
  
  
  ## select needed vars
  df_tmp <- df_raw %>%
    select(wave, !!var_input) %>%
    rename(resp_num = 2) %>%
    mutate(resp_char = haven::as_factor(resp_num))
  
  
  ## extract label for plot title
  var_lab <- str_wrap(sjlabelled::get_label(df_tmp$resp_char), width = 65)
  
  
  ## shorten title for `followsplot`
  title_followspol <- "Do you follow what's going on in government and public affairs?"
  
  
  ## write caption for plot
  caption_dat <- "Data from the Media Exposure and Opinion Formation (MEOF) survey, \n conducted in 8 waves from April 2018 to October 2019 in the U.S."
  
  
  ## clean variable
  df_tmp <- df_tmp %>%
    group_by(wave, resp_char) %>%
    mutate(count = n()) %>%
    ungroup() %>%
    group_by(wave) %>%
    mutate(resp_pct = count / length(resp_char) * 100,
           resp_pct = round(resp_pct, 1),
           #resp_char = haven::as_factor(resp_char),
           resp_char = str_wrap(resp_char, 20),
           wave = paste("Wave ", wave)) %>%
    ungroup() %>%
    unique()
  
  
  ## plot
  p <- ggplot(df_tmp, aes(reorder(resp_char, resp_num), count), fill = as.factor(resp_num)) +
    geom_bar(stat = "identity", position = "dodge") + 
    labs(
      title = var_lab,
      subtitle = str_c("'", var_input, "'"),
      x = "",
      y = "Number of Respondents",
      caption = caption_dat
    ) +
    scale_y_continuous(limits = c(0, max(df_tmp$count)),
                       breaks = seq(0, max(df_tmp$count + 100), by = 200)) +
    facet_wrap(~wave, ncol = 4) +
    theme_classic() +
    theme(plot.title = element_text(size = 14),
          axis.text.x = element_text(angle = 45, hjust = 1, size = 9))
  
  
  ## plot with count labels
  if(share == FALSE) {
    
    p <- p +
      geom_text(aes(resp_char, count, label = count),
                position = position_dodge(0.9),
                vjust = -0.5,
                size = 2)
  }
  
  
  ## plot with share labels
  if(share == TRUE) {
  
    p <- p +
      geom_text(aes(resp_char, count, label = str_c(resp_pct, " %")),
                position = position_dodge(0.9),
                vjust = -0.5,
                size = 2)
  }
  
  
  ## adjust title for `followspol`
  if(var_input == "followspol") {
    
    p <- p +
    labs(title = title_followspol)
  }
  
  
  ## ouput plot
  print(p)
  
}

```
<br>

***

## Test run!

### Some trial and error..
```{r, error=TRUE}

#---- incorrect: `mip` ---------------------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "mip"
share <- TRUE


## try function
super_cool_function(df_input, var_input, share)


#---- incorrect: `birth_year` --------------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "birth_year"
share <- TRUE


## try function
super_cool_function(df_input, var_input, share)


#---- incorrect: `birthyr` -----------------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "birthyr"
share <- TRUE


## try function
super_cool_function(df_input, var_input, share)

```
<br>

### ..but it works!
```{r, echo = TRUE}

#---- correct: impeach_trump ---------------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "impeach_trump"
share <- FALSE


## try function
super_cool_function(df_input, var_input, share)


#---- correct: followspol ------------------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "followspol"
share <- TRUE


## try function
super_cool_function(df_input, var_input, share)


#---- correct: political polarization ------------------------------------------

## specify values for function
df_input <- "data_survey"
var_input <- "issue_political_polarization"
share <- TRUE


## try function
super_cool_function(df_input, var_input, share)

```


