---
title: |
  Hackathon 2023 \
  Task 1.5
author: |
  Author: Giulia Maria Petrilli" \
  Members: Armande Aboudrar-Meda, Giorgio Coppola, Varvara Ilyina, Giulia Petrilli, Luca Vellage
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: FALSE
    theme: cosmo
    toc: TRUE
    toc_depth: 3
    toc_float: true
---
---

```{=html}
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)

options(scipen = 999)
```

```{r, include = T}
pacman::p_load(tidyverse, scales, ggrepel, lemon, RColorBrewer, forcats, plotly, gapminder, gridExtra, patchwork, labelled, haven, ggplot2, dplyr)

options(scipen = 999)
```

<br>

------------------------------------------------------------------------

## Excercise 1.5

The web-tracking data coincides with the fielding of the fourth wave of the survey.
Provide a visualization following the best practices illustrating the breakdown of the
four groups in the data:
• Survey respondents who visited a domain containing “yougov” during the survey
field period
• Survey respondents who did not visit a domain containing “yougov” during the
survey field period despite providing tracking data
• Participants who provided tracking data, but did not participate in the fourth wave
of the survey
• Participants who provided data for the fourth survey wave but no tracking data

```{r}
# load datasets
meof_usa_survey_df <- readRDS("survey/meof_usa_survey_df.RDS") #survey_data 
meof_usa_web_df <- readRDS("tracking/meof_usa_web_df.RDS") #tracking_data
```

```{r}
wave_4_survey <- meof_usa_survey_df %>% # save for later join
  filter(wave == 4) %>% # filter wave 4 out of survey data 
  distinct(personid) %>%  # Keep only distinct person IDs
  mutate(completed_survey = TRUE) # Add a new column indicating completed survey for wave 4

# Calculate timeframes for each wave
# Since a lot of participants appear in multiple wave, i make sure I select the correct rows based on the timeframe matching with wave 4
timeframes_waves <- meof_usa_survey_df %>%
  group_by(wave) %>%              # Group the data by wave
  summarise(min_date = min(starttime),   # Calculate the minimum start date for each wave
            max_date = max(endtime))     # Calculate the maximum end date for each wave

yougov <- meof_usa_web_df %>%
  filter(used_at >= timeframes_waves[timeframes_waves$wave == 4,]$min_date,
         used_at <= timeframes_waves[timeframes_waves$wave == 4,]$max_date) %>%
  mutate(used_yougov = str_detect(domain, "yougov")) %>%
  group_by(personid) %>%
  summarise(used_yougov = sum(str_detect(domain, "yougov")) > 0) %>%
  ungroup() %>%
  mutate(provided_tracking_data = TRUE) %>%
  right_join(tibble(personid = unique(meof_usa_survey_df$personid))) %>% # participants that did not provide tracking data 
  left_join(wave_4_survey) %>%
  mutate(across(c(used_yougov, provided_tracking_data, completed_survey), ~ replace_na(.x, FALSE)))
# `Joining with `by = join_by(personid)` is taken for granted 
```

```{r}
# First and second groups, both from survey data respondents 
# Yougov usage based on people that completed the survey only because the population required in the task is Survey Respondents  
# Select rows where the 'completed_survey' column is TRUE
selected_rows <- subset(yougov, completed_survey == TRUE)
selected_rows$used_yougov <- as.integer(selected_rows$used_yougov)
#yougov$used_yougov <- as.integer(yougov$used_yougov)

# modify dataset yougov for group 3 
# group 3 is: Participants who provided tracking data, but did not participate in the fourth wave of the survey (provided_tracking_data = TRUE, completed_survey = FALSE)
yougov$group3 <- ifelse(yougov$provided_tracking_data == TRUE & yougov$completed_survey == FALSE, 1, 0)

# modify dataset yougov for group 4 
# group 4 is: Participants who provided data for the fourth survey wave but no tracking data  (provided_tracking_data = FALSE, completed_survey = TRUE)
yougov$group4 <- ifelse(yougov$provided_tracking_data == FALSE & yougov$completed_survey == TRUE, 1, 0)

# Set a common Y axis limit for all plots
# This makes comparison easier 
y_axis_limit <- 1500

# First ggplot
plot1_true_completed_survey  <- ggplot(selected_rows, aes(x = factor(used_yougov), fill = factor(used_yougov))) +
  geom_bar(stat = "count", show.legend = TRUE) +
  scale_fill_manual(values = c("red3", "green3"), name = "Used YouGov", labels = c("F", "T")) +
  labs(title = "Survey Participants", x = "Used YouGov domain") +
  theme_minimal() +
  theme(
    text = element_text(size = 10),  # Set the default text size
    plot.title = element_text(size = 12),  # Set the title text size
    axis.title.x = element_text(size = 8),
    legend.position = "bottom",
    legend.text = element_text(size = 8), 
    legend.title = element_text(size = 8),
    legend.key.size = unit(0.3, "cm")
  ) +
  scale_y_continuous(limits = c(0, y_axis_limit))

# Second ggplot
plot2 <- ggplot(yougov, aes(x = factor(group3), fill = factor(group3))) +
  geom_bar(stat = "count", show.legend = TRUE) +
  scale_fill_manual(values = c("red3", "green3"), name = "Tracking no survey", labels = c("F", "T")) +
  labs(title = "All Participants", x = "Supplied web data but no survey") +
  theme_minimal() +
  theme(
    text = element_text(size = 10),  # Set the default text size
    plot.title = element_text(size = 12),  # Set the title text size
    axis.title.x = element_text(size = 7), 
    legend.position = "bottom",
    legend.text = element_text(size = 8), 
    legend.title = element_text(size = 8),
    legend.key.size = unit(0.3, "cm")
  ) +
  scale_y_continuous(limits = c(0, y_axis_limit))

# Third ggplot
plot3 <- ggplot(yougov, aes(x = factor(group4), fill = factor(group4))) +
  geom_bar(stat = "count", show.legend = TRUE) +
  scale_fill_manual(values = c("red3", "green3"), name = "Survey no tracking", labels = c("F", "T")) +
  labs(title = "All Participants", x = "Participate in survey but no tracking data") +
  theme_minimal() +
  theme(
    text = element_text(size = 10),  # Set the default text size
    plot.title = element_text(size = 12),  # Set the title text size
    axis.title.x = element_text(size = 7),
    legend.position = "bottom",
    legend.text = element_text(size = 8), 
    legend.title = element_text(size = 8),
    legend.key.size = unit(0.3, "cm")
  ) +
  scale_y_continuous(limits = c(0, y_axis_limit))

```

```{r}
grid.arrange(plot1_true_completed_survey, plot2, plot3, ncol = 3)
```

