---
title: "Hackathon Project - Task 1.4"
author: |
  Author: Luca Vellage \
  Email: l.Vellage@students.hertie-school.org \
  Group: Armande Aboudrar-Meda, Giorgio Coppola, Varvara Ilyina, Giulia Petrilli & Luca Vellage
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
  pdf_document:
    toc: no
---

```{=html}
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)

options(scipen = 999)
```

------------------------------------------------------------------------

```{r, include = T}
library(tidyverse)
library(dplyr)
library(haven)
library(gt)
library(gtExtras)
```

<br>

## Task: 

### **Perceived hatefulness of social media post**

Create a gt/gtExtras table that reports the aggregated perceived hatefulness of a set of social media posts, following good practice of visualization. For this task, consider the following:

* Some guidance for the data preparation:
+ The content of the social media posts is stored in two types of variables:
vig_{x}_topic and vig_{x}_sender_message. Every respondent evaluated 8 different messages, which is why x goes from 1 to 8. The perception of hatefulness is stored in the variables vig_{x}_hateful.
+ Drop observations where vig_1_hateful is missing.
+ Recode the vig_{x}_topic variables according to the following scheme: gender = "Women", ideologydems = "Democrats", ideologyreps = "Republicans", muslim = "Muslim immigrants".
+ Construct the full content of the message by pasting together the strings of the recoded vig_{x}_topic and vig_{x}_sender_message variables. For instance, one of the full messages reads: “Republicans should be stopped from spreading falsehoods.”
+ For the evaluation, you should average across all evaluated vignettes across all responses, i.e. your unit of analysis is vignettes, not respondents.

* Your table should contain the following information: (1) The message text, (2) the mean and standard deviation of the hatefulness rating by message, and (3) abarplot displaying the distribution of hatefulness ratings 1 to 5 per message.

* The average hatefulness column should be colored by value.

* The table should provide a meaningful title and description, making it a
standalone product that speaks for itself.

------------------------------------------------------------------------

**Loading Data and Selecting Relevant Variables:**
```{r}
meof_usa_survey_df <- read_rds("./survey/meof_usa_survey_df.RDS")

meof_usa_survey_df_1.4 <- meof_usa_survey_df |> 
  select(vig_1_topic, vig_2_topic, vig_3_topic, vig_4_topic, vig_5_topic, vig_6_topic, vig_7_topic, vig_8_topic, 
         vig_1_sender_message, vig_2_sender_message, vig_3_sender_message, vig_4_sender_message, vig_5_sender_message,
         vig_6_sender_message, vig_7_sender_message, vig_8_sender_message, 
         vig_1_hateful, vig_2_hateful, vig_3_hateful, vig_4_hateful, vig_5_hateful, vig_6_hateful, vig_7_hateful, vig_8_hateful)
```

**Cleaning and Prepating Data:**
```{r}

num_vig_groups <- 8
#Function for recoding variable categories
recode_categories <- function(x) {
  recode(x,
         "gender" = "Women",
         "ideologydems" = "Democrats",
         "ideologyreps" = "Republicans",
         "muslim" = "Muslim immigrants")
}

#Clean Dataset
meof_usa_survey_df_1.4_clean <- meof_usa_survey_df_1.4 |> 
  
#Filter missing observations in vig_1_hateful  
  filter(!is.na(vig_1_hateful)) |> 

#Recode variable categories by applying function
  mutate(across(c(vig_1_topic:vig_8_topic),recode_categories)) |> 

#Paste posts together     
  mutate(vig_1_fullpost = paste(vig_1_topic, vig_1_sender_message, sep = " "), 
        vig_2_fullpost = paste(vig_2_topic, vig_2_sender_message, sep = " "), 
        vig_3_fullpost = paste(vig_3_topic, vig_3_sender_message, sep = " "), 
        vig_4_fullpost = paste(vig_4_topic, vig_4_sender_message, sep = " "), 
        vig_5_fullpost = paste(vig_5_topic, vig_5_sender_message, sep = " "),
        vig_6_fullpost = paste(vig_6_topic, vig_6_sender_message, sep = " "), 
        vig_7_fullpost = paste(vig_7_topic, vig_7_sender_message, sep = " "), 
        vig_8_fullpost = paste(vig_8_topic, vig_8_sender_message, sep = " "))

#Select variables that are relevant for the analysis 
meof_usa_survey_df_1.4_analysis <- meof_usa_survey_df_1.4_clean |> 
  select(
    vig_1_fullpost, vig_2_fullpost, vig_3_fullpost, vig_4_fullpost, vig_5_fullpost, vig_6_fullpost, vig_7_fullpost, vig_8_fullpost,
    vig_1_hateful, vig_2_hateful, vig_3_hateful, vig_4_hateful, vig_5_hateful, vig_6_hateful, vig_7_hateful, vig_8_hateful)

```

**Changing Dataset Structure:**
Concept: Change level of analysis from respondent to message
```{r}
#Change dataset structure by using pivotlonger 
meof_usa_survey_df_1.4_analysis_long <- meof_usa_survey_df_1.4_analysis |> 
  pivot_longer(
    cols = contains("fullpost"), 
    names_to = "vignette", 
    values_to = "quote"
  ) |> 
  
#Transform rating variable into numeric 
  mutate(
     across(contains("hateful"), ~ as.numeric(zap_labels(.)))) |> 
  
#Keep only the relevant observations 
  mutate(
    vig_1_hateful = case_when(vignette == "vig_1_fullpost" ~ vig_1_hateful, TRUE ~ NA_real_),
    vig_2_hateful = case_when(vignette == "vig_2_fullpost" ~ vig_2_hateful, TRUE ~ NA_real_),
    vig_3_hateful = case_when(vignette == "vig_3_fullpost" ~ vig_3_hateful, TRUE ~ NA_real_),
    vig_4_hateful = case_when(vignette == "vig_4_fullpost" ~ vig_4_hateful, TRUE ~ NA_real_), 
    vig_5_hateful = case_when(vignette == "vig_5_fullpost" ~ vig_5_hateful, TRUE ~ NA_real_),
    vig_6_hateful = case_when(vignette == "vig_6_fullpost" ~ vig_6_hateful, TRUE ~ NA_real_),
    vig_7_hateful = case_when(vignette == "vig_7_fullpost" ~ vig_7_hateful, TRUE ~ NA_real_),
    vig_8_hateful = case_when(vignette == "vig_8_fullpost" ~ vig_8_hateful, TRUE ~ NA_real_)) |> 
  
  #Rename values in the Vignette column
  mutate(vignette = 
    str_remove(vignette, "_fullpost")) |> 
  
#Create one rating column
  mutate(
    rating = coalesce(vig_1_hateful, 
                      vig_2_hateful, 
                      vig_3_hateful, 
                      vig_4_hateful, 
                      vig_5_hateful, 
                      vig_6_hateful, 
                      vig_7_hateful, 
                      vig_8_hateful)) |> 
  
#Select only the variables relevant for the analysis 
  select(vignette, quote, rating) |> 

#Give unique ID 
  mutate(ID = row_number())
```

**Creating Aggregate Data:**
```{r}
#Create aggregate data
aggregate_var_new <- meof_usa_survey_df_1.4_analysis_long |> 
  group_by(quote) |> 
  summarise(mean_rating = round(mean(rating, na.rm = TRUE), digits = 2), 
            std_dev_rating = round(sd(rating, na.rm = TRUE), digits = 2), 
            respondent_rating = list(rating), .groups = "drop") 
```

**Creating Table with Plots using gt() and gtExtras():**
```{r}
#Create gt table with plot
aggregate_var_new |> 
  gt() |> 
  gt_color_rows(mean_rating, domain = c(1, 5)) |> 
  gt_plt_dist(respondent_rating, type = "histogram", bw = 1, line_color = "black", fill_color = "darkgrey") |> 
  
  tab_header(
    title = "Aggregated Perceived Hatefulness of Social Media Posts",
    subtitle = "Vignette Experiment: Respondents rated 8 different social media posts according to their hatefulness on a scale from 1-5. The table summarizes the mean and standard deviation across all hatefulness ratings and shows the distribution of hatefulness ratings per post.") |> 
  
  tab_footnote(
    footnote = "Source: Media Exposure and Opinion Formation (MEOF)"
  ) |> 

  tab_options(heading.align = "left", 
              heading.title.font.size = 25,
              heading.subtitle.font.size = 13) |> 
  
  cols_label(
    quote = "Message",
    mean_rating = "Mean", 
    std_dev_rating = "Standard Deviation", 
    respondent_rating = "Distribution") |> 
 
  tab_style(
    style = list(
      cell_text(weight = "bold")),
    locations = cells_column_labels(columns = everything()))

```
<br>

Note: Some of the messages used in the Vignette experiment are very similar in spelling and essentially equivalent in meaning. Examples are "Democrats are a stupid animal" and "Democrats are stupid animals". In these cases, the descriptive statistics are, as expected, very similar. Therefore, the phrasing of the messages has **not** been changed for the analysis.




